---
title: "AmazonBeerStudy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r}
# Load necessary Libraries
library(plyr)
library(ggplot2)

# Data Cleanse Function
cleanData <- function(beerList, beerData) {
    # Leave original data the same
    nonDupBeer <- beerData
    # Loop through list of names
    for (name in beerList) {
        # Find beers with the same
        tmpResult <- beerData[which(beerData$Name.x == name), ]
        # print(tmpResult)
        rCount = nrow(tmpResult)
        # print(rCount)
        rNames = rownames(tmpResult)
        # print(rNames)
        
        # Loop through list of beers with same name. If They match on all 4 columns, remove the last beer
        # from the list
        while (rCount > 1) {
            # If name, abv, ibu, and brewery_id are both the same, remove duplicate entry
            if (identical(tmpResult[rCount - 1, "Name.x"], tmpResult[rCount, "Name.x"]) && 
                identical(tmpResult[rCount - 1, "ABV"], tmpResult[rCount, "ABV"]) &&
                identical(tmpResult[rCount - 1, "IBU"], tmpResult[rCount, "IBU"]) &&
                identical(tmpResult[rCount, "Brewery_id"], tmpResult[rCount, "Brewery_id"])) {
                
                # Convert row id to integer
                rmvID <- as.integer(rNames[rCount])
                #cat("Match Found\n")
                #cat("Name: ", name, "\n")
                #cat("Removing row id: ", rmvID, "\n")
                # Duplicate found, remove from beer list
                nonDupBeer <- nonDupBeer[-rmvID, ]
            } else {
                # Display remaining list of duplicates to inspect manually
                if (identical(tmpResult[rCount - 1, "City"], tmpResult[rCount, "City"]) &&
                    identical(tmpResult[rCount - 1, "State"], tmpResult[rCount, "State"])) {
                    
                    #print(tmpResult)
                    #rmvID <- as.integer(rNames[rCount])
                    #cat("Removing: ", name, " ", rmvID, "\n")
                    #nonDupBeer <- nonDupBeer[-rmvID, ]
                    #removalCount = removalCount + 1
                }
            }
            # Reduce count and repeat loop
            rCount = rCount - 1
        }
    }
    # After visual inspection of remaining duplicates that match city and state remove these duplicates
    nonDupBeer <- nonDupBeer[-c(435, 1924, 1262, 779, 951), ]
    # Return list with duplicate beers removed
    return(nonDupBeer)
}
```

# Amazon Beer Study
As part of Amazon's process to select a second headquarters, we have been tasked with analyzing the distribution of breweries, beer, and there ABV and IBV values. There have been studies that correlate states with more breweries and access to higher ABV beers to have happier employees. While this information will not be the final factor for selecting a headquarters, Amazon is exploring all applicable data available to aid in its selection.

As such they have provided us with two files. Breweries.csv which contains a list of all known breweries in the United States and Washington DC. As well as the beers that each brewery makes and their alcholic content. We will be combining these two data sets in order to provide a list of potential states that meet the desired criteria.

# Question 1
``` {r}
# Load in the data sets, UTF-8 encoding necessary due to non-ascii characters being in the data
beers <- read.csv("Beers.csv", header = T, sep = ",", encoding = 'UTF-8')
breweries <- read.csv("Breweries.csv", header = T, sep = ",", encoding = 'UTF-8')

# Change Brew_ID to Brewery_id in order to make merging the two data sets easier
colnames(breweries) <- c("Brewery_id", "Name", "City", "State")

# Clean brewery data
trim.leading <- function (x) sub("^\\s+", "", x)
stateList <- unique(trim.leading(tolower(breweries$State)))

#After uploading the raw brewery data, we counted how many breweries were in each state.
breweries.per.state <- aggregate(data.frame(count=breweries$State), list(value=breweries$State), length)

#We then ordered the data to list number of breweries per state in descending order.
breweries.per.state.ordered <- breweries.per.state[order(-breweries.per.state$count),]
breweries.per.state.ordered
```

# Question 2
``` {r}
# Clean and Combine the two data sets based on the Brewery_id id
# Combine beer and brewery data set
dfMerge <- merge(beers, breweries, by = "Brewery_id", all = T)
# Create list of duplicate beers
beerList <- count(dfMerge, "Name.x")
# Return names of beers with duplicates found
duplicateBeerList <- beerList[(beerList$freq > 1), ]
# Clean the beer data and return
beer_breweries_merge <- cleanData(duplicateBeerList$Name, dfMerge)

# Print the first 6 and last 6 rows of the combined data set
head(beer_breweries_merge, n = 6)
tail(beer_breweries_merge, n = 6)
```

# Question 3
``` {r}
# Count number of NA values for ABV column
NA_in_ABV <- sum(is.na(beer_breweries_merge$ABV))

# Count number of NA values for IBU column
NA_in_IBU <- sum(is.na(beer_breweries_merge$IBU))

# Print count for ABV
print(NA_in_ABV)

# Print count for IBV
print(NA_in_IBU)
```

# Question 4
``` {r}
#We then found the median alcohol by volume (ABV) in the reported beers by each state.
median.abv.per.state <- aggregate(data.frame(median=beer_breweries_merge$ABV), list(value=beer_breweries_merge$State), median, na.rm=TRUE)
names(median.abv.per.state) = c("State", "Median.ABV")

#We then found the median international bitter units (IBU) in the reported beers by each state.
median.ibu.per.state <- aggregate(data.frame(median=beer_breweries_merge$IBU), list(value=beer_breweries_merge$State), median, na.rm=TRUE)
names(median.ibu.per.state) = c("State", "Median.IBU")

#A data frame with just the median calculations per state was made.
median.df <- merge(median.abv.per.state, median.ibu.per.state, by="State")
names(median.df) = c("State", "Median.ABV", "Median.IBU")
median.df.orderedABV <- median.df[order(-median.df$Median.ABV),]
median.df.orderedIBU <- median.df[order(-median.df$Median.IBU),]

library(ggplot2)

#A bar chart was made of the median ABVs per state.
ggplot(data=median.df.orderedABV, aes(x=State, y=Median.ABV)) + geom_bar(stat="identity", fill="steelblue") + geom_text(aes(label=Median.ABV), vjust=-0.3, size=3.5) + theme_minimal() + coord_flip()

#A bar chart was made of the median IBUs per state.
ggplot(data=median.df.orderedIBU, aes(x=State, y=Median.IBU)) + geom_bar(stat="identity", fill="steelblue") + geom_text(aes(label=Median.IBU), vjust=-0.3, size=3.5) + theme_minimal() + coord_flip()
```

# Question 5
``` {r}
# Determine max value of ABV ignoring NAs
abvMax <- max(beer_breweries_merge$ABV, na.rm = T)

# Determine max value of IBU ignoring NAs
ibuMax <- max(beer_breweries_merge$IBU, na.rm = T)

# State with the highest ABV value
abvState <- beer_breweries_merge[which(beer_breweries_merge$ABV == abvMax), ][10]

# State with the highest IBU value
ibuState <- beer_breweries_merge[which(beer_breweries_merge$IBU == ibuMax), ][10]

# Print ABV State
print(abvState)

# Print IBU State
print(ibuState)
```

# Question 6
``` {r}
library(data.table)
NA_in_ABV <- sum(is.na(beer_breweries_merge$ABV))
NA_in_IBU <- sum(is.na(beer_breweries_merge$IBU))
print(NA_in_ABV)
print(NA_in_IBU)
beer_breweries_merged_table <- beer_breweries_merge
colnames(beer_breweries_merged_table)<- c("Brew_ID","Breweries_Name","City","State","Beer_Brand","Beer_ID","ABV","IBU","Style","Ounces")
beer_breweries_merged_table_no_NAs <- beer_breweries_merge[!rowSums((is.na(beer_breweries_merge))),]
summary(beer_breweries_merged_table_no_NAs$ABV)
beer_breweries_merged_table_no_NAs_abv_total <- as.data.table(beer_breweries_merged_table_no_NAs)
class(beer_breweries_merged_table_no_NAs)
beer_breweries_merged_table_no_NAs_abv_total <- beer_breweries_merged_table_no_NAs_abv_total[,sum(ABV), by ="State"]
colnames(beer_breweries_merged_table_no_NAs_abv_total) <- c("State","ABV")
beer_breweries_merged_table_no_NAs_abv_total <- beer_breweries_merged_table_no_NAs_abv_total[order(beer_breweries_merged_table_no_NAs_abv_total$ABV, decreasing = TRUE)]
View(beer_breweries_merged_table_no_NAs_abv_total)
beer_breweries_merged_table_no_NAs_ibu_total <- as.data.table(beer_breweries_merged_table_no_NAs)
beer_breweries_merged_table_no_NAs_ibu_total <- beer_breweries_merged_table_no_NAs_ibu_total[,sum(IBU), by ="State"]
colnames(beer_breweries_merged_table_no_NAs_ibu_total) <- c("State","IBU")
beer_breweries_merged_table_no_NAs_ibu_total <- beer_breweries_merged_table_no_NAs_ibu_total[order(beer_breweries_merged_table_no_NAs_ibu_total$IBU, decreasing = TRUE)]
View(beer_breweries_merged_table_no_NAs_ibu_total)
median.abv.per.state <- aggregate(beer_breweries_merged_table_no_NAs[,7], list(beer_breweries_merged_table_no_NAs$State),median)
colnames(median.abv.per.state) <- c("State","Median ABV")
View(median.abv.per.state)
median.ibu.per.state <- aggregate(beer_breweries_merged_table_no_NAs[,8], list(beer_breweries_merged_table_no_NAs$State),median)
colnames(median.ibu.per.state) <- c("State","Median IBU")
View(median.ibu.per.state)
median_ibu_abv_by_state <- merge(median.abv.per.state,median.ibu.per.state,by="State")
View(median_ibu_abv_by_state)
melted_data <- melt(median_ibu_abv_by_state,id.vars= "State", measure.vars = c("Median ABV","Median IBU"))
colnames(melted_data) <- c("State","Beer_Parameter", "Value")
View(melted_data)
library(ggplot2)
ggplot(melted_data, aes(x= State, y= Value)) + geom_bar(aes(fill = Beer_Parameter), position = "dodge", stat = "identity") + scale_y_log10() + theme(axis.text.x = element_text(angle = 90, hjust= 1.5))
colnames(beer_breweries_merged_table_no_NAs) <- c("Brew_ID", "Brewery_Name", "City", "State", "Beer_Name", "Beer_ID","ABV","IBU","Style","Ounces")
ggplot(beer_breweries_merged_table_no_NAs, aes(x=ABV, y = IBU)) + geom_point()+ geom_smooth(method = lm)
cor.test(beer_breweries_merged_table_no_NAs$ABV, beer_breweries_merged_table_no_NAs$IBU)
lm(beer_breweries_merged_table_no_NAs$ABV ~ beer_breweries_merged_table_no_NAs$IBU )
```