---
title: "Project 2 Long Term Deposits"
author: "Ryan Bass, Brett Benefield"
date: "April 17, 2018"
output: html_document
---
#### Data Set: https://archive.ics.uci.edu/ml/datasets/bank+marketing
#### Source: [Moro et al., 2014] S. Moro, P. Cortez and P. Rita. A Data-Driven Approach to Predict the Success of Bank Telemarketing. Decision Support Systems, Elsevier, 62:22-31, June 2014

# Long Term Deposit Prediction
``` {r echo = TRUE, message = FALSE, warning = FALSE}
# Load libraries
library(ggplot2)
library(randomForest)
library(tidyverse)
library(pROC)
library(shiny)
library(caret)
```

# Executive Summary
The purpose of this data set is to predict whether a client will subscribe to a long term deposit (CD). The data was collected from a Portuguese banking institute which conducted a marketing campaign through phone calls.

# Introduction
Using variables such age, marital status, education, job, duration of the call, we attempted to classify whether a client would sign up for a long term deposit. After initial exploration of the data through plots and graphs we used a random forest model, logistic regression model, and a simplified regression model to aid in this classification. 

```{r, data load initial analysis, echo=TRUE, warning = FALSE}
# Set working directory
setwd("C:\\Users\\STUARTBENEFIELD\\Documents\\SMU\\DDS\\CaseStudy2")

# Read in data set
bank <- read.table("bank-full.csv", sep = ";", header = TRUE)

#intial exploratory plot of age, balance, and the Term Deposit result overlaid
ggplot(bank, aes(x=age, y=balance, color=y)) + geom_point() + scale_y_log10() + theme_gray() + scale_color_manual(values=c("red3", "gold2")) + theme_dark() + labs(title="Age vs. Balance by Term Deposit Result", colour="Deposit Result", x="Age", y="Bank Account Balance")
#note the abrubt lack of people contacted from the bank that are older than 60. Also "yes" seems more prevalent % wise in the greater than 60's and balances above $10.
```

```{r, histogram of age, echo=TRUE}
#histogram of age distribution, and the term deposit result overlaid
ggplot(bank, aes(bank$age, fill=y)) + geom_histogram(bins=77) + scale_fill_manual(values=c("red3", "gold2")) + theme_dark() + labs(title="Age distribution with Term Deposit result overlay", x="Age", y="Count", fill="Deposit Result")
#can see while majority of the ages are in their late 20's and early 30's, the older the customers are the higher % they are to start a term deposit
```

```{r, percent TDs per age range, echo=TRUE}
#to analyze age groups by decades of age have to subset them all into their own dataframe first
bank.olderthan60 <- subset(bank, age >= 60)
bank.btwn50.60 <- subset(bank, age >= 50 & age < 60)
bank.btwn40.50 <- subset(bank, age >= 40 & age < 50)
bank.btwn30.40 <- subset(bank, age >= 30 & age < 40)
bank.btwn20.30 <- subset(bank, age >= 20 & age < 30)
bank.lessthan20 <- subset(bank, age < 20)

#to get percentages of yes's by decades of age
percent.olderthan60.y.yes <- (length(bank.olderthan60$y[bank.olderthan60$y=='yes'])/length(bank.olderthan60$y))*100
percent.btwn50.60.y.yes <- (length(bank.btwn50.60$y[bank.btwn50.60$y=='yes'])/length(bank.btwn50.60$y))*100
percent.btwn40.50.y.yes <- (length(bank.btwn40.50$y[bank.btwn40.50$y=='yes'])/length(bank.btwn40.50$y))*100
percent.btwn30.40.y.yes <- (length(bank.btwn30.40$y[bank.btwn30.40$y=='yes'])/length(bank.btwn30.40$y))*100
percent.btwn20.30.y.yes <- (length(bank.btwn20.30$y[bank.btwn20.30$y=='yes'])/length(bank.btwn20.30$y))*100
percent.lessthan20.y.yes <- (length(bank.lessthan20$y[bank.lessthan20$y=='yes'])/length(bank.lessthan20$y))*100
y.percentages.by.ages <- c(percent.lessthan20.y.yes, percent.btwn20.30.y.yes, percent.btwn30.40.y.yes, percent.btwn40.50.y.yes, percent.btwn50.60.y.yes, percent.olderthan60.y.yes)
age.ranges <- c("<20", "20-30", "30-40", "40-50", "50-60", ">60")
age.ranges <- factor(age.ranges, levels=c("<20", "20-30", "30-40", "40-50", "50-60", ">60"))
y.percentages.by.ages.df <- data.frame(age.ranges, y.percentages.by.ages)

#creating list of n's of the people who started TD per age range
n.of.y.percentages.by.age.range <- c(length(bank.lessthan20$y[bank.lessthan20$y=='yes']), length(bank.btwn20.30$y[bank.btwn20.30$y=='yes']), length(bank.btwn30.40$y[bank.btwn30.40$y=='yes']), length(bank.btwn40.50$y[bank.btwn40.50$y=='yes']), length(bank.btwn50.60$y[bank.btwn50.60$y=='yes']), length(bank.btwn50.60$y[bank.btwn50.60$y=='yes']))

#yes to term deposit by decade age ranges
ggplot(y.percentages.by.ages.df, aes(x=age.ranges, y=y.percentages.by.ages)) + geom_bar(stat="identity", fill="gold2") + theme_dark() + labs(title="Term Deposit % distribution by Age Ranges", y="Term Deposit %", x="Age Range") + geom_hline(yintercept=(100*(length(bank$y[bank$y=='yes'])/length(bank$y))), colour="red3") + annotate("text", x = 1:6, y = 1, label = n.of.y.percentages.by.age.range)
#can see the youngest and oldest age ranges are the highest to agree to a Term Deposit. need to put n's and error bars on this though
```

```{r, percent TDs per education level, echo=TRUE}
#creation of data frames of education level subsets
bank.edu.unk <- subset(bank, education=="unknown")
bank.edu.sec <- subset(bank, education=="secondary")
bank.edu.prim <- subset(bank, education=="primary")
bank.edu.tert <- subset(bank, education=="tertiary")

#solving for percent per education level who enrolled in a Term Deposit
percent.edu.unk.y.yes <- (length(bank.edu.unk$y[bank.edu.unk$y=='yes'])/length(bank.edu.unk$y))*100
percent.edu.sec.y.yes <- (length(bank.edu.sec$y[bank.edu.sec$y=='yes'])/length(bank.edu.sec$y))*100
percent.edu.prim.y.yes <- (length(bank.edu.prim$y[bank.edu.prim$y=='yes'])/length(bank.edu.prim$y))*100
percent.edu.tert.y.yes <- (length(bank.edu.tert$y[bank.edu.tert$y=='yes'])/length(bank.edu.tert$y))*100

#creating a data frame of the education levels, percent that said yes, and the total count per education level
y.percentages.by.edu <- c(percent.edu.unk.y.yes, percent.edu.prim.y.yes, percent.edu.sec.y.yes, percent.edu.tert.y.yes)
edu.level <- c("Unknown", "Primary", "Secondary", "Tertiary")
edu.level <- factor(edu.level, levels=c("Unknown", "Primary", "Secondary", "Tertiary"))
n.per.edu.level <- c(length(bank.edu.unk$y), length(bank.edu.prim$y), length(bank.edu.sec$y), length(bank.edu.tert$y))
y.percentages.by.edu.df <- data.frame(edu.level, y.percentages.by.edu, n.per.edu.level)

#making a string of the total counts of who said yes per job type
n.of.y.percentages.by.edu <- c(length(bank.edu.unk$y[bank.edu.unk$y=='yes']), length(bank.edu.prim$y[bank.edu.prim$y=='yes']), length(bank.edu.sec$y[bank.edu.sec$y=='yes']), length(bank.edu.tert$y[bank.edu.tert$y=='yes']))

#plotting of the % who started a Term Deposit by their education level
ggplot(y.percentages.by.edu.df, aes(x=edu.level, y=y.percentages.by.edu)) + geom_bar(stat="identity", fill="gold2") + theme_dark() + labs(title="Term Deposit % Distribution by Education Level of Customer", y="Term Deposit %", x="Education Level") + geom_hline(yintercept=(100*(length(bank$y[bank$y=='yes'])/length(bank$y))), colour="red3") + annotate("text", x = 1:4, y = 1, label = n.of.y.percentages.by.edu)
```

```{r, percent TDs per employment type, echo=TRUE}
#creation of data frames of job subsets
bank.admin <- subset(bank, job=="admin.")
bank.bc <- subset(bank, job=="blue-collar")
bank.entre <- subset(bank, job=="entrepreneur")
bank.hm <- subset(bank, job=="housemaid")
bank.mgmt <- subset(bank, job=="management")
bank.retired <- subset(bank, job=="retired")
bank.se <- subset(bank,job=="self-employed")
bank.services <- subset(bank, job=="services")
bank.student <- subset(bank, job=="student")
bank.tech <- subset(bank, job=="technician")
bank.unemployed <- subset(bank, job=="unemployed")
bank.unk <- subset(bank, job=="unknown")

#solving for percent per job type who enrolled in a Term Deposit
percent.admin.y.yes <- (length(bank.admin$y[bank.admin$y=='yes'])/length(bank.admin$y))*100
percent.bc.y.yes <- (length(bank.bc$y[bank.bc$y=='yes'])/length(bank.bc$y))*100
percent.entre.y.yes <- (length(bank.entre$y[bank.entre$y=='yes'])/length(bank.entre$y))*100
percent.hm.y.yes <- (length(bank.hm$y[bank.hm$y=='yes'])/length(bank.hm$y))*100
percent.mgmt.y.yes <- (length(bank.mgmt$y[bank.mgmt$y=='yes'])/length(bank.mgmt$y))*100
percent.retired.y.yes <- (length(bank.retired$y[bank.retired$y=='yes'])/length(bank.retired$y))*100
percent.se.y.yes <- (length(bank.se$y[bank.se$y=='yes'])/length(bank.se$y))*100
percent.services.y.yes <- (length(bank.services$y[bank.services$y=='yes'])/length(bank.services$y))*100
percent.student.y.yes <- (length(bank.student$y[bank.student$y=='yes'])/length(bank.student$y))*100
percent.tech.y.yes <- (length(bank.tech$y[bank.tech$y=='yes'])/length(bank.tech$y))*100
percent.unemployed.y.yes <- (length(bank.unemployed$y[bank.unemployed$y=='yes'])/length(bank.unemployed$y))*100
percent.unk.y.yes <- (length(bank.unk$y[bank.unk$y=='yes'])/length(bank.unk$y))*100

#creating a data frame of the job types, percent that said yes, and the total count per job
y.percentages.by.job <- c(percent.admin.y.yes, percent.bc.y.yes, percent.entre.y.yes, percent.hm.y.yes, percent.mgmt.y.yes, percent.retired.y.yes, percent.se.y.yes, percent.services.y.yes, percent.student.y.yes, percent.tech.y.yes, percent.unemployed.y.yes, percent.unk.y.yes)
jobs <- c("Admin", "Blue-collar", "Entrepreneur", "Housemaid", "Management", "Retired", "Self-employed", "Services", "Student", "Technician", "Unemployed", "Unknown")
jobs <- factor(jobs, levels=c("Admin", "Blue-collar", "Entrepreneur", "Housemaid", "Management", "Retired", "Self-employed", "Services", "Student", "Technician", "Unemployed", "Unknown"))
n.per.job <- c(length(bank.admin$y), length(bank.bc$y), length(bank.entre$y), length(bank.hm$y), length(bank.mgmt$y), length(bank.retired$y), length(bank.se$y), length(bank.services$y), length(bank.student$y), length(bank.tech$y), length(bank.unemployed$y), length(bank.unk$y))
y.percentages.by.jobs.df <- data.frame(jobs, y.percentages.by.job, n.per.job)

#making a string of the total counts of who said yes per job type
n.of.y.percentages.by.job <- c(length(bank.admin$y[bank.admin$y=='yes']), length(bank.bc$y[bank.bc$y=='yes']), length(bank.entre$y[bank.entre$y=='yes']), length(bank.hm$y[bank.hm$y=='yes']), length(bank.mgmt$y[bank.mgmt$y=='yes']), length(bank.retired$y[bank.retired$y=='yes']), length(bank.se$y[bank.se$y=='yes']), length(bank.services$y[bank.services$y=='yes']), length(bank.student$y[bank.student$y=='yes']), length(bank.tech$y[bank.tech$y=='yes']), length(bank.unemployed$y[bank.unemployed$y=='yes']), length(bank.unk$y[bank.unk$y=='yes']))

#bar graph of the percent who enrolled in Term Deposit per job type (and their total counts)
ggplot(y.percentages.by.jobs.df, aes(x=reorder(jobs, y.percentages.by.job), y=y.percentages.by.job)) + geom_bar(stat="identity", fill="gold2") + theme_dark() + labs(title="Term Deposit % distribution by Employment Type", y="Term Deposit %", x="Jobs") + geom_hline(yintercept=(100*(length(bank$y[bank$y=='yes'])/length(bank$y))), colour="red3") + annotate("text", x = 1:12, y = 1, label = n.of.y.percentages.by.job) + coord_flip()
```

```{r, percent TDs per marital status, echo=TRUE}
bank.married <- subset(bank, marital=="married")
bank.divorced <- subset(bank, marital=="divorced")
bank.single <- subset(bank, marital=="single")

percent.married.y.yes <- (length(bank.married$y[bank.married$y=='yes'])/length(bank.married$y))*100
percent.divorced.y.yes <- (length(bank.divorced$y[bank.divorced$y=='yes'])/length(bank.divorced$y))*100
percent.single.y.yes <- (length(bank.single$y[bank.single$y=='yes'])/length(bank.single$y))*100

y.percentages.by.marital.status <- c(percent.single.y.yes, percent.married.y.yes, percent.divorced.y.yes)
marital.status <- c("Single", "Married", "Divorced")
marital.status <- factor(marital.status, levels=c("Single", "Married", "Divorced"))
n.per.marital.status <- c(length(bank.single$y), length(bank.married$y), length(bank.divorced$y))
y.percentages.by.marital.status.df <- data.frame(marital.status, y.percentages.by.marital.status, n.per.marital.status)

n.of.y.percentages.by.marital.status <- c(length(bank.single$y[bank.single$y=='yes']), length(bank.married$y[bank.married$y=='yes']), length(bank.divorced$y[bank.divorced$y=='yes']))

ggplot(y.percentages.by.marital.status.df, aes(x=marital.status, y=y.percentages.by.marital.status)) + geom_bar(stat="identity", fill="gold2") + theme_dark() + labs(title="Term Deposit % distribution by Marital Status", y="Term Deposit %", x="Marital Status") + geom_hline(yintercept=(100*(length(bank$y[bank$y=='yes'])/length(bank$y))), colour="red3") + annotate("text", x = 1:3, y = 1, label = n.of.y.percentages.by.marital.status)
```

```{r, percent TDs per month contacted, echo=TRUE}
#when we used machine learning we found particular months were statistically significant as a predictor for Term Deposit
#making subsets by month of the data
bank.jan <- subset(bank, month=="jan")
bank.feb <- subset(bank, month=="feb")
bank.mar <- subset(bank, month=="mar")
bank.apr <- subset(bank, month=="apr")
bank.may <- subset(bank, month=="may")
bank.jun <- subset(bank, month=="jun")
bank.jul <- subset(bank, month=="jul")
bank.aug <- subset(bank, month=="aug")
bank.sep <- subset(bank, month=="sep")
bank.oct <- subset(bank, month=="oct")
bank.nov <- subset(bank, month=="nov")
bank.dec <- subset(bank, month=="dec")

#to get percentages of yes's by given month
percent.jan.y.yes <- (length(bank.jan$y[bank.jan$y=='yes'])/length(bank.jan$y))*100
percent.feb.y.yes <- (length(bank.feb$y[bank.feb$y=='yes'])/length(bank.feb$y))*100
percent.mar.y.yes <- (length(bank.mar$y[bank.mar$y=='yes'])/length(bank.mar$y))*100
percent.apr.y.yes <- (length(bank.apr$y[bank.apr$y=='yes'])/length(bank.apr$y))*100
percent.may.y.yes <- (length(bank.may$y[bank.may$y=='yes'])/length(bank.may$y))*100
percent.jun.y.yes <- (length(bank.jun$y[bank.jun$y=='yes'])/length(bank.jun$y))*100
percent.jul.y.yes <- (length(bank.jul$y[bank.jul$y=='yes'])/length(bank.jul$y))*100
percent.aug.y.yes <- (length(bank.aug$y[bank.aug$y=='yes'])/length(bank.aug$y))*100
percent.sep.y.yes <- (length(bank.sep$y[bank.sep$y=='yes'])/length(bank.sep$y))*100
percent.oct.y.yes <- (length(bank.oct$y[bank.oct$y=='yes'])/length(bank.oct$y))*100
percent.nov.y.yes <- (length(bank.nov$y[bank.nov$y=='yes'])/length(bank.nov$y))*100
percent.dec.y.yes <- (length(bank.dec$y[bank.dec$y=='yes'])/length(bank.dec$y))*100

#making a data frame of the data
y.percentages.by.months <- c(percent.jan.y.yes, percent.feb.y.yes, percent.mar.y.yes, percent.apr.y.yes, percent.may.y.yes, percent.jun.y.yes, percent.jul.y.yes, percent.aug.y.yes, percent.sep.y.yes, percent.oct.y.yes, percent.nov.y.yes, percent.dec.y.yes)
months <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")
months <- factor(months, levels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))
n.per.month <- c(length(bank.jan$y), length(bank.feb$y), length(bank.mar$y), length(bank.apr$y), length(bank.may$y), length(bank.jun$y), length(bank.jul$y), length(bank.aug$y), length(bank.sep$y), length(bank.oct$y), length(bank.nov$y), length(bank.dec$y))
y.percentages.by.months.df <- data.frame(months, y.percentages.by.months, n.per.month)

#creating list of n's of the people who started TD per month
n.of.y.percentages.by.month <- c(length(bank.jan$y[bank.jan$y=='yes']), length(bank.feb$y[bank.feb$y=='yes']), length(bank.mar$y[bank.mar$y=='yes']), length(bank.apr$y[bank.apr$y=='yes']), length(bank.may$y[bank.may$y=='yes']), length(bank.jun$y[bank.jun$y=='yes']), length(bank.jul$y[bank.jul$y=='yes']), length(bank.aug$y[bank.aug$y=='yes']), length(bank.sep$y[bank.sep$y=='yes']), length(bank.oct$y[bank.oct$y=='yes']), length(bank.nov$y[bank.nov$y=='yes']), length(bank.dec$y[bank.dec$y=='yes']))

#plotting of the % who started a Term Deposit in a given month contact was made
ggplot(y.percentages.by.months.df, aes(x=months, y=y.percentages.by.months)) + geom_bar(stat="identity", fill="gold2") + theme_dark() + labs(title="Term Deposit % distribution by Months contact was made", y="Term Deposit %", x="Months") + geom_hline(yintercept=(100*(length(bank$y[bank$y=='yes'])/length(bank$y))), colour="red3") + annotate("text", x = 1:12, y = 1, label = n.of.y.percentages.by.month)
#march, september, october, and december for whatever reason are far above the others. need error bars on this as well
```

```{r, contact vs TD relationships, echo=TRUE}
#contact duration vs. term deposit box plot
ggplot(bank, aes(x=y, y=duration, fill=y, color="white")) + geom_boxplot() + scale_y_log10() + theme_dark() + scale_fill_manual(values=c("red3", "gold2")) + scale_color_manual(values=c("ivory2")) + labs(title="Duration of Contact vs. Term Deposit Outcome", y="Duration of Contact", x="Term Deposit Outcome", fill="Deposit Result") + guides(colour=FALSE)

#duration related to term deposit and contact type
ggplot(bank, aes(x=contact, y=duration, fill=y, color="white")) + geom_boxplot() + scale_y_log10() + theme_dark() + scale_fill_manual(values=c("red3", "gold2")) + scale_color_manual(values=c("ivory2")) + labs(title="Duration of Contact vs. Contact Type", y="Duration of Contact", x="Contact Type", fill="Deposit Result") + guides(colour=FALSE)
```

``` {r}
# Set working directory
setwd("C:\\Users\\STUARTBENEFIELD\\Documents\\SMU\\DDS\\CaseStudy2")

# Read in data set
bankData <- read.table("bank-full.csv", sep = ";", header = TRUE)
```

# Data exploration
``` {r echo = TRUE}
# Explore data
head(bankData)
summary(bankData)
dim(bankData)
```

# Initialize train and test data
``` {r}
# Set seed and create train and test data
set.seed(314)
sampleSize = floor(0.25*nrow(bankData))
indices <- sample(seq_len(nrow(bankData)), size = sampleSize)
train <- bankData[-indices,]
test <- bankData[indices,]
test$y <- factor(test$y)
```

# Random Forest Model
``` {r}
# Create random forest model and descriptive stats
rfModel <- randomForest(as.factor(y) ~ ., data = train, importance = TRUE)
```

### Error Rate %9
``` {r}
print(rfModel)
```

### Explanatory variable importance and ROC curve
``` {r}
round(importance(rfModel), 2)
varImpPlot(rfModel)
plot(rfModel)
predictionProb <- as.data.frame(predict(rfModel, test, type="prob"))
result.roc <- roc(test$y, predictionProb$yes)
plot(result.roc, print.thres="best", print.thres.best.method="closest.topleft")
```

# Logistic Regression Model
``` {r}
# Create Logistic model and descriptive stats
logisticModel <- glm(y ~ ., data = train, family=binomial(link="logit"))
logisticProb <- as.data.frame(predict(logisticModel, test, type = "response"))
colnames(logisticProb) <- c("yes")
```

# ROC curve
``` {r}
result.roc <- roc(test$y, logisticProb$yes)
plot(result.roc, print.thres="best", print.thres.best.method="closest.topleft")
```

# Confusion Table
### Error Rate ~ 10%
``` {r}
threshold <- 0.5
predictedValues <- ifelse(predict(logisticModel, type="response")>threshold, 1, 0)
actualValues <- train$y
table(predictedValues, actualValues)
```

# Model Summary
``` {r}
#summary(logisticModel)
```

# Simplified Logistic Regression Model
``` {r}
# Create a simplified logistic model and descriptive stats
simpleModel <- glm(y ~ duration + month + job + education + marital, data = train, family=binomial(link="logit"))
logisticProb <- as.data.frame(predict(simpleModel, test, type = "response"))
colnames(logisticProb) <- c("yes")
```

# ROC Curve
``` {r}
result.roc <- roc(test$y, logisticProb$yes)
plot(result.roc, print.thres="best", print.thres.best.method="closest.topleft")
```

# Confusion Table
### Error Rate ~ 11%
``` {r}
threshold <- 0.5
predictedValues <- ifelse(predict(simpleModel, type="response")>threshold, 1, 0)
actualValues <- train$y
table(predictedValues, actualValues)
```

# Model Summary
``` {r}
#summary(simpleModel)
```

# Odds
``` {r}
exp(coefficients(simpleModel))
```
Holding all other variables equal, for every one unit increase in duration it is estimated the odds increase by 1%
Holding all other variables equal, it is estimated that month can increase odds as much as 5.6% (March)
Holding all other variables equal, it is estimated job can increase odds as much as 2.13% (Student)
Holding all other variables equal, it is estimated education can increase odds as much as 1.72% (Tertiary)
Holding all other variables equal, it is estimated marital status can increase odds as much as 1.23% (Single)

# Shiny App
``` {r}
# Define Layout
ui <- fluidPage(
  # App Title
  titlePanel('Probability of Long Term Deposit'),
  
  # Left Sidebar
  sidebarLayout(
    # sidebar panel
    sidebarPanel(
      # Duration slider
      sliderInput("duration", label = h3("Call Duration (minutes)"), min = 0, 
                  max = 60, step = .1, value = 0),
      
      # Month Selector
      selectInput("month", label = h3("Select Month:"), 
                  choices = list("January" = "jan", 
                                 "February" = "feb",
                                 "March" = "mar",
                                 "April" = "apr",
                                 "May" = "may",
                                 "June" = "jun",
                                 "July" = "jul",
                                 "August" = "aug",
                                 "September" = "sep",
                                 "October" = "oct",
                                 "November" = "nov",
                                 "December" = "dec"), 
                  selected = "jan"),
      
      # Marital Status    
      selectInput("marital", label = h3("Select Marital Status"),
                  choices = list("Married" = "married",
                                 "Single" = "single",
                                 "Divorced" = "divorced"),
                  selected = "married"),
      
      # Education Level
      selectInput("education", label = h3("Select Education Level"),
                  choices = list("Primary" = "primary",
                                 "Secondary" = "secondary",
                                 "Tertiary" = "tertiary",
                                 "Other" = "unknown"),
                  selected = "primary"),
      
      # Current Job
      selectInput("job", label = h3("Select Current Job Role"),
                  choices = list("Administrator" = "admin.",
                                 "Blue-Collar" = "blue-collar",
                                 "Entrepreneur" = "entrepreneur",
                                 "Housemaid" = "housemaid",
                                 "Management" = "management",
                                 "Retired" = "retired",
                                 "Self-Employed" = "self-employed",
                                 "Services" = "services",
                                 "Student" = "student",
                                 "Technician" = "technician",
                                 "Unemployed" = "unemployed",
                                 "Other" = "unknown"),
                  selected = 1)

      ),
  
      mainPanel(
        h1("The estimated probability is: "),
        h1(textOutput("predict")),
        h3("95% Confidence Interval"),
        h3(textOutput("confidence")),
        plotOutput("plot")
      )
  )
)


# Define Controls
server <- function(input, output) {
  temp <- c()
  month <- c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct","nov","dec")
  simpleModel <- glm(y ~ duration + month + job + education + marital, data = train, family=binomial(link="logit"))
  result <- data.frame("Predict" = 0, "Lower" = 0, "Upper" = 0)
  
  getProb <- reactive({
    prob <- predict(simpleModel, newdata = data.frame(duration = (input$duration*60), month = input$month, job = input$job, 
                                              education = input$education, marital = input$marital), type = "response", se.fit = TRUE)
    result$Predict <- round(prob$fit * 100, 2)
    result$Lower <- round((prob$fit * 100) - (1.96*prob$se.fit), 2)
    result$Upper <- round((prob$fit * 100) + (1.96*prob$se.fit), 2)
    
    return(result)
  })
  
  getPlot <- reactive({
    for (x in 1:12) {
      temp[x] <- predict(simpleModel, newdata = data.frame(month = month[x], job = input$job, duration = (input$duration*60),
                                                           education = input$education, marital = input$marital), type = "response", se.fit = FALSE)[1]
    }
    return(temp)
  })
  
  # Display estimated probability
  output$predict <- renderText({ getProb()[[1]] })
  output$confidence <- renderText({ paste("[", getProb()$Lower, getProb()$Upper, "]") })
  output$plot <- renderPlot({ result <- getPlot()
    plot(1:12, result, ylim=c(0,1), xaxt = "n", main="Probability of Success", xlab="Month", ylab="Probability")
    axis(1, at=1:12, labels=month[1:12])
    lines(1:12, result)
  })
}

# Run App
shinyApp(ui = ui, server = server)
```
